%===============================================================================
\section{Ethical considerations}
\label{section:ethical_considerations}

% Documentation
It is important that everything is openly documented and proper version control is available to ensure transparency, fair play and proof of the true developers. This will be provided by the projects public \href{https://github.com/DVA490-474-Project-Course}{GitHub}\footnote{https://github.com/DVA490-474-Project-Course} page where all code and documentation will be available.
% Sustainability
Proper consideration needs to be taken in regards to the materials used and the disposal of components in the event of replacement or damage. The project will be strict in its disposal and storage of materials and components, following the data sheets and regulations.
% Other fields
Additionally, care must be taken to the possible applications of the research in other fields like warfare and surveillance. The \acs{mit} License will be used to ensure transparency and thus reduce the risk of covert use of the research in unintended ways. 
% Safety and reliability
Finally, proper safety and reliability precautions and practices should be taken to minimise potential damage and harm that the robots can cause. This goes for both damage to robot opponents and disruption of the game, as well as potential harm to humans or the environment. The following precautions and practices will be taken by the project:
\begin{itemize}
    \item Robot status messages will be sent containing information about the status of battery charge and temperatures of microcontroller \acs{cpu}.
    \item Complete stop for a robot if abnormal behaviour is encountered.
    \item Object avoidance
    \item Absolute compliance with data sheets and regulations
\end{itemize}

%===============================================================================