%===============================================================================
\section{Requirement}
\label{section:requirement}

Requirements are necessary to establish in order to ensure that a satisfactory product can be produced and tested, ensuring it meets the original demands placed on the project.

%===============================================================================
\subsection{Product requirements}
\label{subsection:product_requirements}

The following will describe the features, functionality and specifications which the final product must have.

%-------------------------------------------------------------------------------

%\helper{The product specification describes the product that is to be delivered. It is a description of the product in terms of its functionality, performance, quality, etc.}

%===============================================================================
\subsubsection{Functional requirements}

The following functional requirements were established:
\begin{enumerate}
    \item Robot
    \begin{itemize}
        \item Kick the ball towards designated target
        \item Pass the ball towards designated robot
        \item Block ball
        \item Move to designated target
        \item Omnidirectional (holonomic) movement
        \item Not crash into other robots
        \begin{itemize}
            \item Except if it is an attempt at trying to steal the ball from an opponent or to prevent opponents from scoring a goal
            \item Never acceptable if it causes any permanent damage on either robot
        \end{itemize}
        \item Not crash into the arena
        \item React accordingly to referee signals
        \item Send robot status information
        \item Hot-swap battery. The battery should be swappable by plugin in the robot to an alternative source and then changing the battery.
        \item Continuously monitor the capacity of the battery.
        \item Continuously monitor the temperature of the \ac{mcu}.
    \end{itemize}
    \item Centralised strategic planner
    \begin{itemize}
        \item \ac{ai} functionality
        \item Swap field sides on demand
        \item Ensure actions for each robot is not taken from an individualistic point of view, but from a overarching team perspective with a strategic plan aimed at obtaining victory
    \end{itemize}
    \item Simulation interface
    \begin{itemize}
        \item Send packages containing robot commands to grSim
    \end{itemize}
    \item SSL interface
    \begin{itemize}
        \item Receive positional data from ssl-vision
        \item Receive referee commands from ssl-game-controller
        \begin{itemize}
            \item Have AutoReferee functionality
            \item Have humanly operated referee functionality
        \end{itemize} 
    \end{itemize}
    \item Communication protocol
    \begin{itemize}
        \item Wireless
        \item Be peer to peer
        \item Ability to select between two carrier frequencies
    \end{itemize}
    \item Hardware interface
    \begin{itemize}
        \item Control wheel motors
        \item Control kicker
        \item Provide sensor data
        \item Provide robot status information
    \end{itemize}
\end{enumerate}

%-------------------------------------------------------------------------------

%\helper{The functional requirements describe the functions that the product must do.}

%===============================================================================
\subsubsection{Non-functional requirements}

The following non-functional requirements were established:
\begin{enumerate}
    % Individual robot behaviour
    % Collective robot behaviour
    \item The centralised strategy planner must run on a central computer.
    \begin{itemize}
        \item A latency lower than $400\:\text{ms}$ from any point in time at which the centralised strategy planner gives a command until it starts executing on the robot.
    \end{itemize}
    % Simulation
    \item Be able to simulate 12 robots.
    % Simulation interface
    % SSL interface
    % Communication
    \item Communication protocol
    \begin{itemize}
        \item Use WiFi
        \item Use Protobuf
        \item Use \ac{ros2} Humble
        \item $5\%$ dataloss or less
    \end{itemize}
    % Hardware
    \item Each robot must have a reverse polarity protection circuit that changes polarity when the battery is connected incorrectly.
    \item Each robot must have a TVS-diode for over-voltage protection.
    % Wheels
    \item The robot must have four Swedish wheels.
    \item Maximum diameter of each wheel must be $70\:\text{mm}$.
    % Motor
    \item The size of each wheel motor has to be $43\:\text{mm}$ in diameter and $30\:\text{mm}$ in length.
    \item The weight of each motor for the wheels must be less than $200\:\text{g}$.
    \item The voltage of each motor should be capable to handle $24\:\text{V}$ ($6\:\text{S}$ battery).
    % Motor driver
    \item Each motor driver must have work with an input voltage of $24\:\text{V}$ ($6\:\text{S}$ battery).
    \item The weight of each motor driver must be less than $200\:\text{g}$.
    % Dribbler
    \item Minimum \ac{rpm} for the dribbler motor is $10000\:\text{\ac{rpm}}$.
    \item Maximum length of the dribbler motor is $70\:\text{mm}$, excluding the mounting axles.
    % Kicker
    \item The solenoid (kicker) should be capable of launching the ball at a speed of at least $2\:\text{m/s}$.
    \item The solenoid should be capable of handling a voltage of at least $100\:\text{V}$. 
    % Battery
    \item The voltage of the battery in each robot must be $6\:\text{S}$ ($24\:\text{V}$ nominal).
    \item The robot should have battery capacity to continuously operate for $30\:\text{min}$.
    % Sensors
    \item For the break beam sensor detecting if the ball is close to the dribbler the beam cannot be smaller than $3\:\text{mm}$ in diameter.
    % Robot
    \item The robot must fit inside a $180\:\text{mm}$diameter wide and $150\:\text{mm}$ tall cylinder.
    \item Maximum weight of the robot is $5\:\text{kg}$.
    \item The angle between the front wheels is $120\degree$ and between the back wheels the angle is $90\degree$.
    \item Minimum height of the middle plate is $80\:\text{mm}$.
    \item Screws with a uniform diameter should be used, with a minimum size of M3.
    %
    \item The robots \ac{mcu} must process input from sensors and control the motors in less than $40\:\text{ms}$.
    % SSL rules
    \item Comply with all \ac{ssl}-RoboCup rules, see\:\cite{noauthor_rules_2024}.
    \item The vision pattern on the robot must follow the \ac{ssl} rules and fit on the top plate.
    \item The colour markings on top of the robot must comply with \ac{ssl} rules.
\end{enumerate}

%-------------------------------------------------------------------------------

%\helper{The non-functional requirements describe the technical specifications of the product in details: e.g. colors, performance, quality metrics.}

%===============================================================================
\subsection{Project requirements}

The project has locked time and cost, focus will thus be placed on scope to ensure the project does not expand unrealistically, resulting in an inability to deliver the product. The following list describes what must be done in the project to be able to deliver the product:
\begin{itemize}
    \item Limit the project as described in Limitations, see section\:\ref{section:limiations}.
    \item Keep to the scope of the project as described in Scope, see section\:\ref{section:scope}. 
    \item Keep within budget, see Project budget, section\:\ref{section:project_budget}.
    \item Facilitate clear and good communication within the team and with the sponsor.
\end{itemize}

%-------------------------------------------------------------------------------

%\helper{Requirements on the execution and prioritization between the project’s triple constraints.}

%===============================================================================
\subsection{Prerequisites}

The project demands that the sponsors provide the hardware team with full access to the $\text{B.nr}\:326$ workshop and the tools and machines that should be present there. If additional training is required to operate these tools and machines, then the project demands that this training be afforded to the hardware team latest 2024-10-10.

%-------------------------------------------------------------------------------

%\helper{Demands on the project’s sponsor/owner or client that have to be achieved to ensure the project’s execution and result.}

%===============================================================================