%===============================================================================
\section{Staffing}
\label{section:staffing}

The staffing plan, in terms of the staff and their roles, were arranged by external sources (sponsor), however tasks were assigned internally based on qualification, collaboration and each team members wishes. The roles and tasks of each project member can be seen in Table.\:\ref{tab:contributors_roles}.

%------------------------------------------------------------------------------

%\helper{Example of a staffing plan, add references to other plans that might include additional information. }

%===============================================================================
\subsection{Roles, responsibilities and authorities}
\label{section:staffing_roles_responsibilities_and_authorities}

%The project teams, and their tasks, have been organised to try to ensure good collaboration, effective use of the members skills and qualifications, as well as their wishes. 
Three authoritative roles with their own responsibilities were assigned (by the sponsor):
\begin{itemize}
    \item Team Leader: Responsible for guiding and coordinating the group to achieve a common goal. A team leader is also responsible for making plans, assigning tasks, ensuring team collaboration, solving conflict, motivating the group and making key decision. One of the main responsibilities of a team leader is to communicate between the team and stakeholders, ensuring that the development process follows the broader project vision.  
    \item Software lead: Organises the software team to ensure work continues smoothly and that the software requirements are met. This includes scheduling, overseeing the software teams progress, planning the software layout and thorough inspection of standards and requirements. 
    \item Hardware lead: Manages the hardware team by overseeing the tasks, provide planning and making sure all requirements are met.
\end{itemize}

%------------------------------------------------------------------------------

\begin{comment}
Our project team structure is specifically crafted to leverage the distinctive skills and capabilities of each team member, fostering effective teamwork. The key roles, responsibilities, and authorities in our project include:

\begin{itemize}
    \item \textbf{Software (SW) Team Lead:} Leads the software team, responsible for overseeing all activities related to software development, ensures that software requirements are met and coordinates with the developers on the software team.
    \item \textbf{Hardware (HW) Team Lead:} Leads the hardware team, responsible for all activities related to hardware development, ensures that hardware requirements are met and coordinates with the developers on the hardware team.
    \item \textbf{Software (SW) Developer:} Implements software components, conducts testing and debugging, and addresses software-related issues.
    \item \textbf{Hardware (HW) Developer:} Designs, tests, and debugs hardware components, addresses hardware-related issues.
\end{itemize}
\end{comment}

%===============================================================================
\subsection{Staffing plan}

The staffing plan is described in Table.\:\ref{tab:contributors_roles}.

%------------------------------------------------------------------------------

\begin{comment}
Our staffing plan assigns roles to each member of our project team as follows:

\begin{itemize}
    \item Stieg Larsson - Software Team Lead
    \item Astrid Lindgren - Hardware Team Lead
    \item Henning Mankell - Software Developer
    \item Selma Lagerlöf - Hardware Developer
\end{itemize}

Each individual was chosen for their role based on their skills, experience, and interest in the project. Regular meetings will be held to ensure that everyone is on track and to address any concerns that may arise.
\end{comment}

%===============================================================================